Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
multi-action
Simplify Stencil Computation definition

  Absolute index is a constant integer expression relative to the enclosing
  loop.
\end{definition}

@@

\begin{definition}[Stencil computations]
\label{def:stencil}
  Let $a$ be an array of dimensionality $n$ and $\overline{b}$ a
  collection of arrays of arbitrary (possible differing)
  dimensionalities.
  A \emph{stencil computation} comprises an iteration by a set $I$ of at
  most $n$ induction variables
  over a subset of the index space of $a$. Each step of the interation
  determs the elements of $a$ by an
  assignment $a(\bar{e}) = e_r$ where each $e \in
  \bar{e}$ is either a neighbourhood or constant index.
  For all arrays $b \in \bar{b}$ and array subscripts $b(\bar{e}')$ in
  $e_r$ and that flow to $e_r$, then each $e' \in \bar{e}'$ is also
  either a neighbourhood or constant index.

@@

% 2. Break down of "interesting specifications" (contain more than
% just reflexive)
%   - Single-action, histogram on depths

@@

%   - Single-action + irreflexives, histogram on depths
%   - Bounded specs (how many lower, upper, or both)

>>>>

  \emph{Absolute index} is a constant integer expression relative to the
  enclosing loop.
\end{definition}

@@

\begin{definition}[Stencil computations]
\label{def:stencil}
  Let $a$ be an array of dimensionality $n$ and $\overline{b}$ a
  collection of arrays of arbitrary (possibly differing)
  dimensionalities.
  A \emph{stencil computation} comprises an iteration by a set $I$ of at
  most $n$ induction variables
  over a subset of the index space of $a$. Each iteration
  determines the elements of $a$ by an
  assignment $a(\bar{e}) = e_r$ where each $e \in
  \bar{e}$ is either a neighbourhood or constant index.
  For all $b \in \bar{b}$ and array subscripts $b(\bar{e}')$
  that flow to $e_r$, each $e' \in \bar{e}'$ is
  either a neighbourhood or absolute index.

@@

% 2. Break down of "interesting specifications" (contain more than
% just reflexive)
%   - Single-action, histogram on depths
%   - Single-action + irreflexives, histogram on depths

@@

    % multiAction: 156
    % multiActionMulOnly: 146
A multi-action specification consists of at least two uses of forward,
backward, or centered regions, and can be combined with any number of
reflexive regions. We identified 156 multi-action specifications out
of which 146 had regions combined only with $\term{*}$.

%   - Bounded specs (how many lower, upper, or both)
